---
name: Cleyton Farias
position: "Data Scientist and Ph.D. Candidate in Economics"
address: "Recife, Pernambuco"
profilepic: "cleyton3.jpg"
phone: +21 81 99821 4643
www: cleytonfar.github.io
email: "cleytonfarias@outlook.com"
github: cleytonfar
linkedin: cleyton-farias-51b064161
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
```



# Education
```{r}
tribble(
  ~ degree, ~ uni, ~ loc, ~ dates, 
  "Ph.D. Candidate in Economics", "Universidade Federal de Pernambuco", "Recife - PE", "Mar. 2017 - Mar. 2021 (expected)", 
  
  
  "Master of Science in Economics", "Universidade Federal de Pernambuco", "Recife - PE", "Mar. 2015 - Feb. 2017",

  "Bachelor of Science in Economics", "Universidade Federal de Pernambuco", "Recife - PE", "Mar. 2010 - Feb. 2014"
  
) %>% 
  detailed_entries(degree, dates, uni, loc)
```


# Experience

```{r}
tribble(
  ~ role, ~ company, ~ loc, ~ dates, ~ details,
  "Data Scientist Consultant", "Kurier Tecnologia e Inteligência Jurídica", "Recife - PE", "S1 2018 - Present",
  "Predictive Analysis",
  
  "Data Scientist Consultant", "Ministério da Cultura do Brasil", "Brasília-DF & Recife-PE", "S1 2018 - S4-2018",
  "Centro de Artes e Esportes Unificados (CEUS) Report",
  
  "Data Scientist Consultant", "Ministério da Cultura do Brasil", "Brasília-DF & Recife-PE", "S2 2017 - S4-2017",
  "Motion Picture Industry Report",

  "Teaching Assistant", "Universidade Federal de Pernambuco", "Recife-PE", "July 2016 - Dec 2016", 
  "Macroeconomics: Graduate level; Prof.  Paulo Henrique Vaz; PIMES/UFPE.",
  
  "Teaching Assistant", "Universidade Federal de Pernambuco", "Recife-PE", "July 2016 - Dec 2016", 
  "Macroeconomics: Graduate level; Prof.  Paulo Henrique Vaz; PPGGES/UFPE.",
  
  "Teaching Assistant", "Universidade Federal de Pernambuco", "Recife-PE", "2014", 
  "Macroeconomics II: Undergraduate level; Prof. Marcelo Eduardo da Silva. Economics Department/UFPE.",
  
  "Teaching Assistant", "Universidade Federal de Pernambuco", "Recife-PE", "2012", 
  "Introduction to Macroeconomics: Undergraduate level; Prof. André Magalhães. Economics Department/UFPE.",
 
 "Teaching Assistant", "Universidade Federal de Pernambuco", "Recife-PE", "2011", 
 "Introduction to Microeconomics: Undergraduate level; Prof. Andrea Sales S. de Melo; PPGGES/UFPE."
 
) %>% 
  detailed_entries(role, dates, company, loc, details)
```


# Research Interest

1. **Main**: Machine Learing; Deep Learning; Data Science.
2. **Secondary**: Applied Econometrics; Policy Evaluation; Computational Economics;


# Awards & Achievements

## Scholarships
```{r}
tribble(
  ~ scholarship, ~ from, ~ year,
  "Ph.D. scholarship from Brazilian Council for Scientific and Technological Development", "CNPq", "2017-2012",
  "M.S. scholarship from Brazilian Council for Scientific and Technological Development ", "CNPq", "2015-2017"
) %>%
  brief_entries(scholarship, year, from)
```


## Competitions
```{r}
tribble(
  ~ competition, ~ from, ~ year,
  "Top 5% placed in Titanic:  Machine Learning from Disaster, Machine Learning competition", "Kaggle", "2018",
  
  "Top 10% placed in Pover-T Tests:  Predicting Poverty, Machine Learning competition", "Driven Data", "2018"
  
) %>%
  brief_entries(competition, year, from)
```

\newpage


# Additional Information

 * **Programming Languages Skill**: R, Julia, C, Python, SQL, LateX;
 * **Technologies**: Linux, Git, PostgreSQL, Elasticsearch, Kibana;
 * **Complementary Courses**:
    1.  Practical Machine Learning by Johns Hopkins University - Coursera (2018);
    2.  Complete Elasticsearch Masterclass with Logstash and Kibana - Udemy (2018);
    3.  Regression Models by Johns Hopkins University - Coursera (2018);
    4.  The Complete SQL Bootcamp - Udemy (2018);
    5.  Joining Data in PostgreSQL - DataCamp (2018);
    6.  Intro to SQL for Data Science - DataCamp (2018);
    7.  Statistical Inference by Johns Hopkins University - Coursera (2018);
    8.  Reproducible Research by Johns Hopkins University - Coursera (2018);
    9.  Exploratory Data Analysis by Johns Hopkins University - Coursera (2018);
    10.  Getting and Cleaning Data by Johns Hopkins University - Coursera (2018);
    11.  R Programming by Johns Hopkins University - Coursera (2018);
    12.  The Data Scientists Toolbox by Johns Hopkins University - Coursera (2018);
    13.  Machine Learning Toolbox - DataCamp (2018);
    14.  Unsupervised Learning in R - DataCamp (2018);
    15.  Supervised Learning in R: Case Studies.  - DataCamp (2018);
    16.  Supervised Learning in R: Regression.  - DataCamp (2018);
    17.  Supervised Learning in R: Classification.  - DataCamp (2018);
    18.  Cluster Analysis in R. - DataCamp (2018);
    19.  Advanced Econometrics, Graduate Program in Economics - Universidade Federal de Pernambuco (2017);
    20.  Topics in Nonparametric Statistics and Machine Learning, Graduate Program in Statistics - UniversidadeFederal de Pernambuco (2017);
    21.  Computational Statistics, Graduate Program in Statistics - Universidade Federal de Pernambuco (2017);
    22.  Advanced R Programming - Udemy (2017);
    23.  R Data Pre-Processing & Data Management - Udemy (2017);
    24.  R Programming - Udemy (2017);
    25.  Shell Scripting - Udemy (2016);
    26.  Programming, Undergraduate Program in Computer Science - Universidade Federal de Pernambuco(2013);
    27.  Times Series, Undergraduate Program in Statistics - Universidade Federal de Pernambuco (2013);
    28.  Econometrics Methods, Undergraduate Program in Statistics - Universidade Federal de Pernambuco(2013)


